Assignment 5

### 2015-02-25 rmtw/a5/latex8.tex
Started planning

\textbf{Planning the review}
\begin{itemize}
\item Identification of the need for a review (5.1)
Check other SLRs in the field and evaluate them
\item Commissioning a review (5.2)
not needed
\item Specifying the research question(s) (5.3)
this is very important :)
the search process must identify primary studies that address the research questions
the data extraction process must extract the data items needed to answer the questions
the data analysis process must synthesise the data in such a way that the questions can be answered.

read the questions in 5.3.1 to come up with similar ones for readability

>>>>

\textbf{Planning the review}
Initially, existing SLRs were identified and evaluated, with the goal of mapping and identifying the gap in the existing literature. All identified SLRs \cite{santiagion2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiagion2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}. Based on these results, the need to evaluate previous research on model driven \textit{software} development was identified.

The next step was to define the research questions. The main research question was constructed to create a wide scope to be able to investigate which characteristics are most vital to consider when adopting MDSD. The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are condering to implement MDSD.

\begin{itemize}
